What Does Reproducible Research Mean for Plant Pathology?

### 2016-07-06 README.rmd
Move Reproducible_Research.rmd to README.rmd
When knitting the Rmd file keep the md file, so a README.md file is
generated, which is the whole matter of the manuscript.

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "5 July 2016"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
bibliography: bibliography.bib
csl: phytopathology.csl
---

>>>>

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "5 July 2016"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
    keep_md: TRUE
bibliography: bibliography.bib
csl: phytopathology.csl
---
